---
title: "R Notebook"
output: html_notebook
---

# **Anime Recommendation**

In this project, I have tried to Do some EDA. and created an recommendation system

For this project, the given dataset contains information on user preference data from 73,516 users on 12,294 anime. Each user is able to add anime to their completed list and give it a rating and this data set is a compilation of those ratings.

### Imporing Libraries
```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(plotly)
library(readr)
library(data.table)
library(ggcorrplot)
library(gridExtra)
library(Matrix)
library(splitstackshape)
```

### Importing Dataset
```{r warning=FALSE}
# Anime Dataset
anime <- read_csv("C:/LOCAL_R/Rishabh##/Machine Learning/data SET/anime-recommendations-database/anime.csv")

# Rating Dataset
rating <- read_csv("C:/LOCAL_R/Rishabh##/Machine Learning/data SET/anime-recommendations-database/rating.csv")
```


### Understanding the Dataset
```{r}
# Structure of Dataset
glimpse(anime)
glimpse(rating)
# Dimension of Dataset
dim(anime)
dim(rating)
```

Before doing any anlysis we will first seperate all the genres.
```{r}
# Splitting Genre
# library(splitstackshape)
anime <- cSplit_e(anime, "genre", ",", type = "character", fill = 0)
anime <- anime[,c(-3)]
```

### **Data Visualization**

#### **Univariate Analysis**

##### Continuous Variables
```{r}
# Count missing Values
na_count <-sapply(anime, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)

# Anime Dataset
# Comverting episodes into numeric type
anime$episodes <- as.numeric(as.factor(anime$episodes))

p11 <- ggplot(anime, aes(episodes)) +
      geom_histogram( fill = "springgreen4", na.rm = TRUE,binwidth = 1)+ ylim(0,250) + scale_x_continuous(breaks = seq(0,200, by =50))

p12 <-ggplot(anime, aes(rating)) +
      geom_histogram( fill = "deeppink3", na.rm = TRUE,binwidth = 0.05) + scale_x_continuous(breaks = seq(0,10, by =0.5))

p13 <-ggplot(anime, aes(members)) +
      geom_histogram( fill = "darkorchid", na.rm = TRUE,binwidth = 5000)+ ylim(0,50) + scale_x_continuous(breaks = seq(0,1000000, by =100000))

grid.arrange(p11,p12,p13, nrow = 2, top = "Continuous Variable")

```

##### Categorical Variables
```{r}

# Type
ggplot(anime, aes(fct_infreq(as.factor(type)),fill = type)) +
  geom_bar(na.rm = TRUE) + xlab("Type") + ggtitle("Anime Types")

# Genre count of 1's
genre_count_matrix <- t(anime[,-c(1:6)] %>% summarise_all(funs(sum))%>% sort(decreasing = T))
# Geting rownames from genre_count_matrix
genre_names <- rownames(genre_count_matrix)
# Creating dataFrame from genre_count_matrix
genre_count <- data_frame(genre_names = as.factor(genre_names),genre_count = genre_count_matrix[1:43])
# Sort Values by Genre Count
genre_count <- genre_count[order(genre_count$genre_count),]

# Ploting
ggplot(genre_count, aes(y=genre_count,x=genre_names,fill = genre_names)) + geom_bar(stat="identity") + ggtitle("Anime Genres")+ theme(legend.position="none",axis.text.x=element_text(angle=30, hjust=1))


```

#### **Bivariate Analysis**
```{r}

```



















